Statistical performance analysis of data-driven neural mass models

### 2013-08-22 manuscript/manuscript.tex
edits to dicussion

\section{Discussion}

extensions to other applications e.g. experimental design

algorithm performance

@@

we say nothing about how algorithms will work with uncertainty in the actual model -- thus can be considered a ``best case'' situation, where we know the true model exactly.

>>>>

\section{Discussion}
\brian{Brief Summary of Paper}
This paper has introduced a method for evaluating Bayesian estimation algorithms for fitting neural mass models to electrophysiological data. The results demonstrate that it is feasible to recover three neural mass models from data, assuming the model is accurate.

\brian{Feasibility of Models}
We have demonstrated how the method can be used to test the feasibility of recovering the states of models from data. In other words, the method can be used to see if a model is too complex to be recovered data regardless of the estimation method. If the measurement has no /or little information about the states then the bound will be infinitely high.

\brian{Is there a better observation to improve estimation? / experimental design}
The BCRLB can improve experimental design, where the bound can be used to select what is important to measure. For example, 
sampling rate affects the CRLB, extensions to other applications e.g. experimental design
adaptive sensing

\brian{Calculating this provides an extra layer of intuition into the estimation process}
The evolution of the bound over time provides indication of convergence properties

derivatives higher -> more information

\brian{Stimulation / Excitation to maximize information}
Probing - maybe

\brian{Is there a better estimator?}
algorithm performance bench marking

\brian{Not model section}
Best case analysis which assumes the data comes from the model
we say nothing about how algorithms will work with uncertainty in the actual model -- thus can be considered a ``best case'' situation, where we know the true model exactly.
Model section still needs to be done by checking how the models can predict the behavior of the system, check need to be checked experimentally.

\brian{This method is the standard in radar and tracking and papers will not get published without it}
This is the first point of call for benchmarking estimation and tracking algorithms in the radar applications (refs). We argue that this should also be the case for neural state estimation and tracking. Neuroscience stands to benefit greatly from estimation and control techniques from engineering

\brian{Big picture}
Find the right level of model complexity and measurements to get to the truth.

\brian{What a subject specific model will provide the scientist and the neurologist}

@@
